An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-05-01 VLDB2026/main.tex
Update main.tex

	Lastly, our findings show that the distribution and the \textcolor{blue}{ number} of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods. Enhancing the robustness of these algorithms under diverse data conditions is another key challenge that warrants further investigation.

	\section{CONCLUSION}
	\textcolor{blue}{In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries. We enrich the dataset with attribute information and design diverse experimental settings. We analyze the performance of these algorithms in depth. We find that these algorithms have different strengths and weaknesses under large-scale data, complex queries, and resource-constrained scenarios. Attribute filtering algorithms show clear limitations in flexibility and Boolean logic support. Range filtering algorithms show weaknesses in multi-attribute queries and high-recall performance. Sometimes, baseline methods like Faiss perform better in high-recall settings. In the future, we need to improve the flexibility and robustness of attribute filtering algorithms and enhance the performance of range filtering algorithms.}
%	\textcolor{blue}{
%		In this paper, we evaluate hybrid query methods, including algorithms, vector databases, and libraries. We design experiments to assess the performance of attribute filtering algorithms. We enrich existing datasets with attribute values and create various experimental scenarios to ensure fair comparisons. We run experiments on 7 real-world datasets to analyze the effectiveness of attribute filtering algorithms. We also compare range filtering algorithms using 4 range query datasets. Finally, we analyze the results, summarize key findings, and identify areas for improvement. Our study validates previous research and provides insights for future work.
%	}
%

>>>>

	Lastly, our findings show that the distribution and the number of attributes, as well as dataset properties (e.g., dimensionality and LID), significantly impact the performance of attribute filtering methods. Enhancing the robustness of these algorithms under diverse data conditions is another key challenge that warrants further investigation.

	\section{CONCLUSION}
	In this paper, we systematically evaluate hybrid query methods, including various algorithms, vector databases, and libraries. We enrich the dataset with attribute information and design diverse experimental settings. We analyze the performance of these algorithms in depth. We find that these algorithms have different strengths and weaknesses under large-scale data, complex queries, and resource-constrained scenarios. Attribute filtering algorithms show clear limitations in flexibility and Boolean logic support. Range filtering algorithms show weaknesses in multi-attribute queries and high-recall performance. Sometimes, baseline methods like Faiss perform better in high-recall settings. In the future, we need to improve the flexibility and robustness of attribute filtering algorithms and enhance the performance of range filtering algorithms.
%	\textcolor{blue}{
%		In this paper, we evaluate hybrid query methods, including algorithms, vector databases, and libraries. We design experiments to assess the performance of attribute filtering algorithms. We enrich existing datasets with attribute values and create various experimental scenarios to ensure fair comparisons. We run experiments on 7 real-world datasets to analyze the effectiveness of attribute filtering algorithms. We also compare range filtering algorithms using 4 range query datasets. Finally, we analyze the results, summarize key findings, and identify areas for improvement. Our study validates previous research and provides insights for future work.
%	}
%
